Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Fix fig 8 caption.

\begin{figure*}
  \centering
  \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
  \caption{Raster and compressed sensing images of a 5 micron square
    area of the CS-20NG grating. All images are 512$\times$512 pixels:
    the raster images marked as 64 and 128 lines have been
    interpolated. The rows of pixels indicated by the red line are
    shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
  \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
    area of the CS-20NG grating. All images are 512$\times$512 pixels.
    The rows of pixels indicated by the red lines are
    shown in Fig.~\ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}
